---
title: "AboutMYapp"
author: "Kidpea LAU"
date: "2018Äê10ÔÂ23ÈÕ"
output: slidy_presentation
runtime: shiny
---

## R Markdown

This is an R Markdown presentation about the app i produced lately.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## THE app

- show the scatter plot of random pionts with the middle piont u can choose.
- calculate the size of the scatter.


## Slide with R Output

```{r echo=FALSE}
library(shiny)

sliderInput("bins",
                   "Number of bins:",
                   min = -50,max=50,value = 100)
numericInput("Num","Input the population U want(0~100)",value = 100,min=0,max = 100,step = 1)

numericInput("Mid","Decisede the middle value (-50~50)",value = 50,min = -50,max=50)
       
 
```


```{r echo=FALSE}
renderPlot({
    # generate bins based on input$bins from ui.R
    NumOfP<-input$Num
    meanOfP<-input$Mid
    maxX<-input$bins
    X<-rnorm(NumOfP,mean = meanOfP,sd=maxX)
    Y<-rnorm(NumOfP,mean = meanOfP,sd=maxX)
    
    # draw the histogram with the specified number of bins
    plot(X,Y)
    
  })
model1<-reactive({
    maxX<-input$bins
    pred<-maxX*maxX
  })
output$pred<-renderText({
    model1()
  })

 
```

##Thanks 
have a nice day
